True versus apparent shapes of astrophysical bow shocks

### 2016-04-28 papers/Paper1/sec-application.tex
Insert conic xi figures

With this we can use the results of section \ref{sec:conic} to estimate the projected conic shapes for bow shocks with different winds momenta and different density distributions. In figure () we show 
the theoretical conic curves for different vales of $\beta$ with a fixed $\xi$

>>>>

With this we can use the results of section \ref{sec:conic} to estimate the projected conic shapes for bow shocks with different winds momenta and different density distributions. 
In figure (\ref{fig:conic-xi}) we show the theoretical conic curves for different vales of $\beta$ with a fixed $\xi$. Most of the proplyds fit well with a elliptic-like conic shape.
LV4 is a special case which fits better with an hyperbola

\begin{figure*}
\begin{tabular}{cc}
\includegraphics[width=0.48\linewidth]{../../read-shapes/conic_xi-10} & \includegraphics[width=0.48\linewidth]{../../read-shapes/conic_xi-08} \\
\includegraphics[width=0.48\linewidth]{../../read-shapes/conic_xi-06} & \includegraphics[width=0.48\linewidth]{../../read-shapes/conic_xi-04} 
\end{tabular}
\label{fig:conic-xi}
\caption{Comparison of projected radii for conic models against with the observed proplyds. A fixed value of $\xi$, which describes the anisotropy of the inner wind, is used
in each graph. Models with $\theta_c > 0$ correspond to elliptical-like shapes, while $\theta_c<0$ describes hyperbolic-like shapes.}
\end{figure*}
